---
title: "MS4"
author: "Jason Yoo"
date: "3/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
# Loading libraries

library(janitor)
library(tidyverse)
```
```{r data, include = FALSE}
## Loading Human vs. Human dataset

lichess <- read.csv("data/games.csv") %>% clean_names()

# Loading Computer vs. Computer dataset

internet_c <- read.csv("data/big_datasets/2016_CvC.csv") %>% clean_names()

# Loading Computer vs. Human dataset

internet_h <- read.csv("data/big_datasets/2016_CvH.csv") %>% clean_names()

# Merging the internet datasets into one

internet <- rbind(internet_c, internet_h)

# Splitting the strings in column 'moves'

test <- str_split(internet$moves[1], ' ')[[1]]

# Removing the unnecessary move orders

test2 <- test[-seq(1, length(test), 3)]
```
\n
The data above was gotten from https://data.world/thule179/2016-internet-chess-games, and it is a dataset of internet chess games on the internet chess server in the year 2016. The lichess data was taken from lichess.org, a popular online chess site. So far, I have started cleaning the data in the cvc and cvh datasets. This began with using the clean_names function in the Janitor package, and renaming strings in the moves column.

The moves in the cvc and cvh data are listed in numeric order, ie. 1. 'first move' 2. 'second move', and so on. The lichess dataset is listed as 'first move' 'second move' and so the number listings in the two latter datasets must be removed in order for analyzing the data in a uniform fashion. In addition, I have merged cvc and cvh into one database, and created a column denoting whether the game was played against a computer or a human.

The preliminary goal for this project is to analyze which beginning moves result in the greatest success, or wins, in chess games. I hypothesize that it will be different according to whether it is a computer playing against a computer, a computer playing against a human, and a human playing against a human. This is because computers thinking... well, computationally, while humans are much more prone to acting on a subconscious instinct or a "gut feeling." Obviously, computers will have a much more robust storage of good opening repertoire -- I would also like to compare their move choices with humans.